\Large Bayes network classifiers for fRMI

### 2012-09-14 proposal/proposal.tex
Added info to application section

This project is about classifying fMRI data in order to detect the cognitive states associated with viewing different stimuli. Specifically, viewing sentences versus viewing pictures will evoke different patterns of activity in the brain. By using classifiers we will try to capture these patterns by predicting which stimuli a participant is looking at, based on the brain activity during that time.

@@

Explain how you get data or simulator, how many examples, how many inputs, outputs, whether it is an RL, classification, or regression problem.

@@

\section{Setup of Experiments}

@@

>>>>

This project is about classifying fMRI data in order to detect the cognitive states of subjects associated with viewing different stimuli. Specifically, viewing sentences versus viewing pictures will evoke different patterns of activity in the brain. By using classifiers we will try to capture these patterns by predicting which stimuli a participant is looking at, based on the brain activity during that time.

@@

For our project, we are using a collection of data from the StarPlus project\footnote{StarPlus project - http://www.cs.cmu.edu/afs/cs.cmu.edu/project/theo-81/www/}. This dataset contains the results from a trial experiment performed at Carnegie Mellon University. The data was originally collected my Marcel Just \textit{et al}.

The dataset contains data on 6 test subjects that each completed a number of trials. For each trial (see section \ref{sec:setup}), 54 fMRI snapshots were made of specific regions of their brain. Each snapshot consists of a list of 3d pixels (so called voxels). The dimensions of these snapshots are 64x64x8 voxels, amounting to a total of 5700 voxels per snapshot (this is less than 64 * 64 * 8 because only specific regions were recorded).

Along with each snapshot, metadata is available on the state of the trial (e.g. what stimulus was active?) and what user the snapshot belongs to. For each entire trial, we also have data on the trial specifics and the result of the trial.

Since we will be trying to classify trial snapshots to determine what stimulus was active when the snapshot was taken, our application deals with a typical classification problem.

@@

\section{Setup of Experiments}
\label{sec:setup}

@@

22nd/24th - presentation
31st - final document
